\textbf{Preprinting Microbiology}

### 2017-04-20 submission/Schloss_PrePrints_mBio_2017.tex
Final edits to manuscript

\textbf{Number of words:} \textasciitilde4500 plus references, figures, and abstract

@@

The field of microbiology has experienced significant growth due to
transformative advances in technology and the influx of scientists
driven by a curiosity to understand how microbes interact with each
other and their environment to sustain myriad biochemical processes that
are essential for maintaining the Earth. With this explosion in
scientific output, a significant bottleneck has been the ability to
disseminate this new knowledge to peers and the public in a timely
manner. Preprints have emerged as a tool that a growing number of
microbiologists are using to overcome this bottleneck. Furthermore,
posting preprints can help to transparently recruit a more diverse pool
of reviewers prior to submitting to a traditional journal. Although use
of preprints is still limited in the biological sciences, early
indications are that preprints are a robust tool that can complement and
enhance peer-reviewed publications. As publishing moves to embrace
advances in internet technology, there are many opportunities for
preprints and peer-reviewed journals to coexist in the same ecosystem.

@@

\textbf{\emph{Background.}} Many scientists, including microbiologists,
have begun to use preprints and other online venues such as social
media, blog posts, and videos as methods to garner attention for their
research and to engage the public. A preprint is an interim research
product, such as an unpublished manuscript, made publicly available
before going through an official peer-review process (1--4). Authors can
post their manuscript to a preprint server for others to read, share,
and comment. Preprints were initially adopted among physicists and
biologists in the 1960s as a method of sharing interesting research
amongst colleagues (5). While the biological community's commitment to
preprints waned, the physics community adopted what is now the
\emph{arXiv} (pronounced ``archive'') preprint server that was hosted at
the Los Alamos National Laboratories from 1991 to 1999 and then at
Cornell University (6). For some physicists and mathematicians, posting
a preprint to \emph{arXiv} optionally followed by submission to a
peer-reviewed journal has become a standard publication pathway.
Although \emph{arXiv} has hosted a number of computational biology
papers, the server has not drawn widespread attention from biologists.
Among proponents of \emph{arXiv}, preprints have aided in the
development of research communication by accelerating the release of the
science and helping it to achieve a wider audience for critique and
reception (7). Considering the broadening adoption of preprints among
microbiologists, I sought to explore the specific uses of and concerns
regarding preprints.

\textbf{\emph{Landscape of preprint servers.}} In 2013, two preprint
servers, the \emph{bioRxiv} (pronounced ``bio-archive'') and \emph{PeerJ
Preprints}, were launched as preprint servers for biologists that would
parallel \emph{arXiv} (8). Both platforms offer similar features:
preprint posting is free; each preprint receives a digital object
identifier (DOI) that facilitates the ability to cite preprints in other
scholarly work; if the preprint is ever published, the preprint is
linked to the published version; the submission process for both options
is relatively simple allowing authors to upload a PDF version of their
preprint and supplemental materials; preprints are typically publicly
available in about 24 hours; they have built-in venues for authors to
discuss their research with people who leave comments on the manuscript;
preprints undergo a basic screening process to remove submissions with
offensive or non-scientific content; and the sites provide article-level
metrics indicating the number of times an abstract has been accessed or
the preprint has been downloaded. There are several important
differences between the two options. First, \emph{PeerJ Prints} is a
for-profit organization and \emph{bioRxiv} is a non-profit organization
sponsored by Cold Spring Harbor Laboratory. This difference can be
meaningful to authors since some journals, including the American
Society for Microbiology (ASM) Journals, will only accept submissions
that have been posted on preprint servers hosted by non-profit
organizations. Second, preprints at \emph{PeerJ Preprints} are posted
under the Creative Commons Attribution License (CC-BY) and
\emph{bioRxiv} preprints can be posted under one of four CC-BY licenses
or with no permission for reuse. This can be relevant for authors hoping
to submit their work to a journal as journals will not consider
manuscripts posted as preprints under a CC-BY license (e.g.
\emph{Proceedings of the National Academy of Sciences}). The flexibility
of the \emph{bioRxiv} licensing empowers authors to choose the model
that best suits them, while ensuring the rapid posting of their research
results; however, it is important to provide clear information to
authors on the legal and practical tradeoffs of each option. A cosmetic,
but still relevant difference between the two is the layout and feel of
the two websites. Compared to the \emph{bioRxiv} site, the \emph{PeerJ
Preprint} site is more fluid, gives readers the ability to ``follow'' a
preprint, and provides better access to article keywords and the ability
to search preprints. With broader acceptance of preprints by traditional
journals, many journals, including all of the ASM journals, have
established mechanisms to directly submit manuscripts that are posted as
preprints on \emph{bioRxiv}. The only direct submission mechanism for
manuscripts submitted at \emph{PeerJ Preprint} is to the \emph{PeerJ}
journal. In many ways, preprint servers have taken on the feel of a
journal. As adoption of this approach expands, it is likely that the
features of these sites will continue to improve. It is also worth
noting that numerous other opportunities exist for other forms of
interim research products (e.g.~blog posts, videos, protocols, etc.) to
obtain DOIs that make the work citable. As these possibilities increase,
the preprint landscape risks becoming fractured.

One solution to the fracturing of the preprint landscape would be
indexing sites that allow a user to easily search for content across the
preprint landscape. Several examples of these efforts already exist and
it likely that these interfaces and their ability to span the landscape
will improve. For example, although Google Scholar includes preprints
hosted at \emph{bioRxiv} and \emph{PeerJ Preprints} in their search
results, PubMed and Web of Science do not. A relatively new example of
what this might look like is PrePubMed
(\url{http://www.prepubmed.org/}), which seeks to index preprints from
numerous sources. A more organized effort is being initiated with
funding through ASAPbio to create a ``Central Service'' that would
aggregate preprints in the life sciences (\url{http://asapbio.org}).
There is also hope that the National Institutes of Health (NIH) will
renew their interest in indexing preprints as separate research products
than peer-reviewed publications. As preprint servers and other content
providers begin to look and act like traditional journals by
incorporating features and interfaces, it is important to value the
strength of the preprint - that of an interim research product, nimble
and quickly posted. It is therefore essential to balance the
requirements placed on authors for features associated with preprints
with the current desirable efficiency of the preprint format.

\textbf{\emph{Specific challenges for microbiology.}} Although preprints
offer an efficient and novel venue for disseminating microbiology
research, there are several considerations that the scientific community
and those that oversee preprint servers must consider. It is critical
that assurances be given that policies are in place to address these
issues. First, a significant amount of attention has to be given to the
potential dual use research of concern (DURC) since posted results in
microbiology research could offer insights to individuals seeking to
engage in terrorist activities. Second, for researchers engaging in
research that involves human subjects it is critical that assurances be
made that institutional review boards have been consulted and have
approved of the research. Third, there is significant concern regarding
researchers hiding potential conflicts of interest that could affect a
project's experimental design, analysis, and interpretation of results.
Finally, recent expansions in scientific publishing have revealed
numerous cases of plagiarism or misconduct. Again, while hoping to
maintain the efficiency of the preprint format, traditional microbiology
journals have policies for these issues in place that should be easy to
implement by preprint servers. It is possible that if preprint usage
continues to expand, many of these problems may also grow as has been
experienced in the expansion of the traditional publishing industry.

\textbf{\emph{Acceptance of preprints by journals.}} An early
controversy encountered by researchers interested in posting their work
as preprints as a stage in disseminating their research was whether it
constituted prior publication (9). The broad consensus of the
International Committee of Medical Journal Editors and numerous journals
is that preprints do not constitute prior publication (10). This
consensus is reflected in the current policies of journals that commonly
publish microbiology research including those published by ASM, the
Microbiology Society, International Society for Microbial Ecology, PLOS,
the \emph{Proceedings of the National Academy of Science},
\emph{Science}, \emph{Nature}, \emph{Journal of Infectious Diseases},
and Cell press. Each take a generally permissive stance towards posting
of preprints prior to submission. Considering the relatively fluid
nature of many of these policies and the journals' specific policies,
prospective authors should be aware of the positions taken by the
journals where they may eventually submit their work. Comprehensive
lists of journals' attitudes towards preprints are available online and
are regularly updated (11, 12).

\textbf{\emph{Preprints and peer-review.}} The use of preprints for
citations in other scientific reports and grant proposals has recently
been called into question (13). It is important to note that the
peer-review process was adapted to the technologies and trends that have
evolved over the past 100 years. The formal peer-review system that most
journals currently use was not developed until the end of the 1800s with
the advent of typewriters and carbon paper (14). Editorial decisions
were typically made by a single person or a committee (i.e.~the
editorial board) who had an expertise that covered the scope of the
journal. As science became more specialized, new journals would form to
support and provide a source of validation to the new specialty. The
growth in science in the mid 1900s resulted in a shift from journals
struggling to find sufficient numbers of manuscript to publish to having
too many manuscripts submitted. It has been argued that the widespread
adoption of decentralized peer-review was due to the increased
specialization and to deal with the large number of manuscript
submissions (15). Peer-review did not achieve widespread use at many
journals, including the \emph{Journal of Bacteriology}, until the 1940s
and 1950s. Thus the ``tradition'' of peer-review is only 70 years old.
Given the rapid advances in communication technology and even greater
specialization within microbiology, it is worth pondering whether the
current scientific publishing system and peer-review system, in
particular, need to continue to adapt with our science.

Communicating research has traditionally been done within research group
meetings, departmental seminars, conferences, and as publications. Along
this continuum, there is an assumption that the quality of the science
has been improved because it has been vetted by more experts in the
field. The public dissemination of one's research is a critical
component of the scientific method. By describing their research,
scientists subject their work to formal and informal peer review. Their
research is scrutinized, praised, and probed to identify questions that
help seed the next iteration of the scientific method. A common critique
of more modern approaches to publishing has been an inability to assess
the quality of the science without the validation of peer-review.
Attached to assertions of the validity of the research has been
assertions of the impact and robustness of the research. These are all
quality assessments that many acknowledge are difficult to assess by the
traditional peer-review process. This has led to some journals, most
notably \emph{PLOS ONE}, calling for referees to place a reduced
emphasis on the perceived impact or significance of the work. It has
also led to the call for replacing or complementing pre-publication
peer-review with post-publication peer-review using PubMed Commons,
PubPeer, journal-based discussion forums, F1000Research, and other
mechanisms. Alas if scientists are going to depend on post-publication
peer-review or informal methods of peer-review for documents like
preprints, they must be willing to provide constructive feedback on the
work of others.

@@

First, a common concern is that if a researcher posts their work as a
preprint, it will be ``scooped'' by another researcher and the preprint
author will lose their ability to claim primacy or their ability to
publish the work in a journal. Considering the preprint is a citable
work with a DOI, it would, in fact, be the preprint author that scooped
the second. Furthermore, a preprint could prevent getting scooped since
a preprint would indicate to others in the field that the work had
already been done, which would prevent wasted time and effort. The use
of preprints uncouples the communication of the discovery from the
relevance of the discovery, which will come later based on peer-review,
comments from other scientists at meetings or online, and eventually
citations. A growing number of scientific societies and journals,
including ASM view preprints as citable and as having a legitimate claim
to primacy (1, 16--18). Some scientists worry that with such protection
a researcher can make a claim without valid data to support their claims
(3). This is possible; however, it is also the responsibility of the
scientific community to utilize the peer-review mechanisms that are
available to comment on those preprints pointing out methodological
problems or to indicate that they are speaking beyond the data. As
preprints gain broader adoption, the tension between establishing
primacy and the completeness of the preprint may test the policies of
preprint-friendly journals.

A second area of concern is whether a preprint can be used to support a
grant proposal. Given the length limitations placed on grant proposals
by funding agencies, there is a push to cite previous work to indicate a
research team's competence in an area or to provide preliminary data.
Some fear that the use of preprints will allow scientists to circumvent
page limits by posting preliminary manuscripts. One would hope that both
consumers of preprints and grant proposal reviewers would be able to
differentiate between someone trying to game the system and someone that
is using preprints as a mechanism to improve their science. This would
be greatly facilitated if funding agencies would include preprints as
evidence for research progress, but listed separately from peer-reviewed
publications to help review panels in their decisions and to help author
substantiate evidence they feel they need to provide.

A third concern is what role preprints should have in assessing a
scientist's productivity. Clearly use of publication metrics as an
indicator of a scientist's productivity and impact is a contentious
topic without even discussing the role of preprints. Regardless, given
the propensity for researchers to list manuscripts as being ``in
preparation'' or ``in review'' on an application or curriculum vitae,
listing them instead as preprints that can be reviewed by a committee
would significantly enhance an application and a reviewer's ability to
judge the application. In fact, several funding agencies including the
Wellcome Trust and the UK Medical Research Council encouraging
fellowship applicants to include preprints in their materials;
meanwhile, the NIH is in the process of soliciting input from the
scientific community on their role in grant applications. Others are
mandating that researchers post preprints for all of their work prior to
submitting the work to a journal (19).

Beyond these concerns, preprints are also causing some to change their
publication goals. Some authors are explicitly stating that a preprint
will not be submitted to a journal (20). Although these authors may be a
minority of those who post preprints, such an approach may be attractive
to those who need to cite a report of a brief research communication, a
critique of another publication, or negative results. It is clear that
the adoption of preprints will challenge how scientists interact and
evaluate each other's work. There is great potential to empower
researchers by controlling when a citable piece of work is made public.

\textbf{\emph{Microbiology anecdotes.}} The peer-review editorial
process can be lengthy and adversarial. In contrast, preprints represent
a rapid and potentially collaborative method for disseminating research.
Several anecdotes from the microbiology literature are emblematic of
benefits of the rapid release cycle that is inherent in the use of
preprints.

First, preprints have proven useful for rapidly disseminating results
for disease outbreaks and new technologies. Prior to the recent Zika
virus outbreak there were approximately 50 publications that touched on
the biology and epidemiology of the virus; as of March 2017 the number
of Zika virus-related publications was over 2,000. During the recent
outbreak, more than 130 Zika virus-related preprints have been posted at
\emph{bioRxiv}. Any manuscript that was published went through several
month delays in releasing information to health care workers, the
public, and scientists needing to learn new methods to study a
previously obscure virus. In contrast, those that posted their work as a
preprint were able to disseminate their methods and results instantly.
Another interesting use of preprints to disseminate new information
about Zika virus has been the posting of a preprint describing the Zika
virus outbreak in the US Virgin Islands that will be continually updated
as new data and analyses are performed (21). Over the last several years
there have also been rapid advances in DNA sequencing technologies that
have fundamentally changed how microbial science is performed. One
notable technology, the MinIon sequencing platform from Oxford Nanopore,
has received considerable attention from researchers who have posted
more than 100 preprints describing new MinIon-based methods and results
to preprint servers. For such a rapidly developing technology, the
ability to share and consume methods from other scientists has created a
feed forward effect where the technology has likely advanced at a faster
rate than it otherwise would have.

Second, preprints have proven useful for rapidly correcting the
scientific literature. On February 9, 2015, \emph{Cell Systems} posted a
study by Afshinnekoo et al. online (22). The study collected and
analyzed metagenomic sequence data from the New York City subway system
and reported finding \emph{Yersinia pestis} and \emph{Bacillus
anthracis}. Because of the focus on these two bioterrorism agents, this
study generated a considerable amount of media attention. On April 25,
2015, Petit et al. (23) posted a preprint to Zenodo demonstrating that
there was no evidence for \emph{B. anthracis} in the dataset. On July
29, 2015, a critique was published by \emph{Cell Systems} along with a
response from the original authors offering a correction to their
manuscript (24, 25). A second anecdote of using preprints to aid in
post-publication peer-review surrounds the publishing of a draft
tardigrade genome in \emph{The Proceedings of the National Academy of
Sciences}. On November 23, 2015 a study by Boothby et al. (26) was first
published online. The authors claimed that 17.5\% of its genes came from
bacteria, archaea, fungi, plants, and viruses. Another group had been
analyzing sequence data from a parallel tardigrade genome sequencing
project and did not observe the same result. A week later, on December
1, 2015, the second group had posted a preprint comparing the two genome
sequences and demonstrating that the exciting claims of horizontal gene
transfer were really the product of contaminants (27); this analysis
would eventually be published online by the original journal on March
24, 2016 followed by a rebuttal by the original authors on May 31, 2016
(28, 29). Two other analyses of the original data were published in May
2016 and a third was posted as a preprint on February 2, 2016 (30--32).
These anecdotes underscore the value of having a rapid posting cycle to
correcting errors in the scientific literature and that results posted
to preprint servers were able to correct the record within weeks of the
initial publication while the traditional path took six months in both
cases. A final notable case where preprints have accelerated the
correction of the scientific record was a preprint posted by Bik et al.
(33) reporting numerous cases of image manipulation in peer reviewed
studies. This was a case where a journal may have been reluctant to
publish the findings because it could have put the journal in a bad
light. Posting the manuscript as a preprint removed potential conflicts
of interests from journals that could have hindered its ability to be
published. After the preprint was posted on April 20, 2016 it was
published in \emph{mBio} on June 7, 2016 (34). Instead of using
preprints to react to published papers that have been through peer
review, it would be interesting to consider how the editorial process
for these examples and the infamous ``Arsenic Life'' paper (35) would
have been different had they initially been posted as preprints.

>>>>

\textbf{Counts:} \textasciitilde5600 words plus 50 references, 1 figure, and a 150 word abstract

@@

The field of microbiology has experienced significant growth due to
transformative advances in technology and the influx of scientists
driven by a curiosity to understand how microbes sustain myriad
biochemical processes that maintain the Earth. With this explosion in
scientific output, a significant bottleneck has been the ability to
rapidly disseminate new knowledge to peers and the public. Preprints
have emerged as a tool that a growing number of microbiologists are
using to overcome this bottleneck. Posting preprints can help to
transparently recruit a more diverse pool of reviewers prior to
submitting to a journal for formal peer-review. Although use of
preprints is still limited in the biological sciences, early indications
are that preprints are a robust tool that can complement and enhance
peer-reviewed publications. As publishing moves to embrace advances in
internet technology, there are many opportunities for preprints and
peer-reviewed journals to coexist in the same ecosystem.

@@

\textbf{\emph{Background.}} A preprint is an interim research product
that is made publicly available before going through an official
peer-review process with the goals of soliciting feedback, accelerating
dissemination of results, establishing priority, and publicizing
negative results (1--5). Authors can post their manuscript to a preprint
server for others to read, share, and comment. In the 1960s, Information
Exchange Groups were the first formal attempt to broadly disseminate
paper-based preprints among physicists and biologists (6, 7). Although
the biological community's commitment to preprints waned by 1967, the
physics community persisted and eventually adopted what is now the
\emph{arXiv} (pronounced ``archive'') preprint server that was hosted at
the Los Alamos National Laboratories from 1991 to 1999 and then at
Cornell University (8). For some physicists and mathematicians, posting
a preprint to \emph{arXiv} optionally followed by submission to a
peer-reviewed journal has become a standard publication pathway.
Although \emph{arXiv} has hosted a number of computational biology
preprints, the server has not drawn widespread attention from
biologists. Among proponents of \emph{arXiv}, preprints have aided in
the development of research communication by accelerating the release of
science and helping authors reach a wider audience for critique and
establishment of priority (9). Considering the broadening adoption of
preprints among microbiologists, I sought to explore the specific uses
of and concerns regarding preprints.

\textbf{\emph{Landscape of preprint servers.}} In 2013, two preprint
servers, the \emph{bioRxiv} (pronounced ``bio-archive'') and \emph{PeerJ
Preprints}, were launched as preprint servers for biologists that would
parallel \emph{arXiv} (10). According to information provided on the
\emph{bioRxiv} and \emph{PeerJ Preprints} websites and my personal
experiences, both platforms offer similar features: preprint posting is
free; each preprint receives a digital object identifier (DOI) that
facilitates the ability to cite preprints in other scholarly work; if
the preprint is ever published, the preprint is linked to the published
version; the submission process for both options is relatively simple
allowing authors to upload a PDF version of their preprint and
supplemental materials; preprints are typically publicly available in
about 24 hours; they have built-in venues for authors to discuss their
research with people who leave comments on the manuscript; preprints
undergo a basic screening process to remove submissions with offensive
or non-scientific content; and the sites provide article-level metrics
indicating the number of times an abstract has been accessed or the
preprint has been downloaded. There are several important differences
between the two options. First, \emph{PeerJ Prints} is a for-profit
organization and \emph{bioRxiv} is a non-profit organization sponsored
by Cold Spring Harbor Laboratory. This difference can be meaningful to
authors since some journals, including the American Society for
Microbiology (ASM) Journals, will only accept submissions that have been
posted on preprint servers hosted by not-for-profit organizations (11).
Second, preprints at \emph{PeerJ Preprints} are posted under the
Creative Commons Attribution License (CC-BY) and \emph{bioRxiv}
preprints can be posted under one of four CC-BY licenses or with no
permission for reuse. This can be relevant for authors hoping to submit
their work to \emph{Proceedings of the National Academy of Sciences} as
the journal will not consider manuscripts posted as preprints under a
CC-BY license. The NIH encourages authors to post preprints under the
CC-BY or public domain licenses (5). The flexibility of the
\emph{bioRxiv} licensing empowers authors to choose the model that best
suits them, while ensuring the rapid posting of their research results;
however, it is important to provide clear information to authors on the
legal and practical tradeoffs of each option. A cosmetic, but still
relevant difference is the layout and feel of the two websites. Compared
to the \emph{bioRxiv} site (Figure S1), the \emph{PeerJ Preprint} site
is more fluid, gives readers the ability to ``follow'' a preprint, and
provides better access to article keywords and the ability to search
preprints (Figure S2). With broader acceptance of preprints by
traditional journals, many journals, including all of the ASM journals,
have established mechanisms to directly submit manuscripts that are
posted as preprints on \emph{bioRxiv}. The only direct submission
mechanism for manuscripts submitted at \emph{PeerJ Preprint} is to the
\emph{PeerJ} journal. In many ways, preprint servers have taken on the
feel of a journal. As adoption of this approach expands, it is likely
that the features of these sites will continue to improve. It is also
worth noting that numerous other opportunities exist for other forms of
interim research products (e.g.~blog posts, videos, protocols, etc.) to
obtain DOIs that make the work citable. As these possibilities increase,
the preprint landscape risks becoming fractured.

One solution to the fracturing of the preprint landscape would be the
creation of indexing sites that allow a user to easily search for
content across multiple preprint servers. Several examples of these
efforts already exist and it is likely that these interfaces and their
ability to span the landscape will improve. For example, although Google
Scholar includes preprints hosted at \emph{bioRxiv} and \emph{PeerJ
Preprints} in their search results, PubMed and Web of Science do not. A
relatively new example of what this might look like is PrePubMed (12),
which seeks to index preprints from numerous sources. A more organized
effort is being initiated with funding through ASAPbio to create a
``Central Service'' that would aggregate preprints in the life sciences
(13). As preprint servers and other content providers begin to look and
act like traditional journals by incorporating features and interfaces,
it is important to value the strength of the preprint - that of an
interim research product that is nimble and quickly posted. It is
therefore essential to balance the requirements placed on authors for
features associated with preprints with the efficiency of the preprint
format.

\textbf{\emph{Specific challenges for microbiology.}} Although preprints
offer an efficient and novel venue for disseminating microbiology
research, there are several considerations that the scientific community
and those that oversee preprint servers must consider. It is critical
that assurances be given that policies are in place to address these
issues and that these policies are made transparent. First, attention
has to be given to dual use research of concern (DURC) since
microbiology-related research could offer insights to individuals
seeking to engage in inappropriate activities. Second, for researchers
engaging in research that involves human subjects and other vertebrates,
it is critical that assurances be made that institutional oversight
committees have been consulted and have approved of the research. Third,
there is significant concern regarding researchers disclosing potential
conflicts of interest that could affect a project's experimental design,
analysis, and interpretation of results. Finally, recent expansions in
scientific publishing have revealed numerous cases of plagiarism or
misconduct. Again, while hoping to maintain the efficiency of the
preprint format, traditional microbiology journals have screening
procedures and oversight committees that address these issues. Similar
efforts need to be implemented by preprint servers. As preprint usage
continues to expand many of these problems may also grow similar to the
experiences within the traditional publishing industry has expanded.

\textbf{\emph{Acceptance of preprints by journals.}} An early
controversy encountered by researchers interested in posting their work
as preprints as a stage in disseminating their research was whether it
constituted prior publication (14). The broad consensus of the
International Committee of Medical Journal Editors and numerous journals
is that preprints do not constitute prior publication (15). This
consensus is reflected in the current policies of journals that commonly
publish microbiology research including those published by ASM, the
Microbiology Society, International Society for Microbial Ecology, PLOS,
the \emph{Proceedings of the National Academy of Science},
\emph{Science}, \emph{Nature}, \emph{Journal of Infectious Diseases},
and Cell press. Each take a generally permissive stance towards posting
of preprints prior to submission. Comprehensive lists of journals'
attitudes towards preprints are available online and are regularly
updated (16, 17). Considering the relatively fluid nature of many of
these policies and the journals' specific policies, prospective authors
should be aware of the positions taken by the journals where they may
eventually submit their work.

\textbf{\emph{Preprints and peer-review.}} The use of preprints for
citations in other scientific reports and grant proposals has recently
been called into question (18). It is important to note that the
peer-review process was adapted to the technologies and trends that have
evolved over the past 100 years. The formal peer-review system that most
journals currently use was not developed until the end of the 1800s with
the advent of typewriters and carbon paper (19). Editorial decisions
were typically made by a single person or a committee (i.e.~the
editorial board) who had an expertise that covered the scope of the
journal. As science became more specialized, new journals would form to
support and provide a source of validation to the new specialty. The
growth in science in the mid 1900s resulted in a shift from journals
struggling to find sufficient numbers of manuscript to publish to having
too many manuscripts submitted. It has been argued that the widespread
adoption of decentralized peer-review was due to the increased
specialization and to deal with the large number of manuscript
submissions (20). Peer-review did not achieve widespread use at many
journals, including the \emph{Journal of Bacteriology}, until the 1940s
and 1950s. Thus the ``tradition'' of peer-review is only 70 years old.
Given the rapid advances in communication technology and even greater
specialization within microbiology, it is worth pondering whether the
current scientific publishing system and peer-review system, in
particular, need to continue to adapt with our science.

Communicating research has traditionally been done within research group
meetings, departmental seminars, conferences, and as publications. Along
this continuum, there is an assumption that the quality of the science
has been improved because it has been vetted by more experts in the
field. The public dissemination of one's research is a critical
component of the scientific method. By describing their research,
scientists subject their work to formal and informal peer-review. Their
research is scrutinized, praised, and probed to identify questions that
help seed the next iteration of the scientific method. A common critique
of more modern approaches to publishing has been an inability to assess
the quality of the science without the validation of peer-review.
Attached to assertions of the validity of the research has been
assertions of the impact and robustness of the research. These are all
quality assessments that many acknowledge are difficult to assess by the
traditional peer-review process. This has led to some journals, most
notably \emph{PLOS ONE}, calling for referees to place a reduced
emphasis on the perceived impact or significance of the work. It has
also led to the call for replacing or complementing pre-publication
peer-review with post-publication peer-review using PubMed Commons,
PubPeer, journal-based discussion forums, F1000Research, and other
mechanisms. Alas if scientists are going to depend on post-publication
peer-review or informal methods of peer-review for documents like
preprints, they must be willing to provide constructive feedback on the
work of others.

@@

First, a common concern is that if a researcher posts their work as a
preprint, it will be ``scooped'' by another researcher and the preprint
author will lose their ability to claim primacy or their ability to
publish the work in a journal. Considering the preprint is a citable
work with a DOI, it would, in fact, be the preprint author that scooped
the second. Furthermore, a preprint could prevent getting scooped since
a preprint would indicate to others in the field that the work had
already been done, which would prevent wasted time and effort. The use
of preprints uncouples the communication of the discovery from the
relevance of the discovery, which will come later based on peer-review,
comments from other scientists at meetings or online, and eventually
citations. A growing number of scientific societies and journals,
including ASM view preprints as citable and as having a legitimate claim
to primacy (1, 21--23); however, it remains to be determined whether the
journals will stand by these policies. Some scientists worry that with
such protection a researcher can make a claim without valid data to
support their claims (3). This is possible; however, it is also the
responsibility of the scientific community to utilize the peer-review
mechanisms that are available to comment on those preprints pointing out
methodological problems or to indicate that they are speaking beyond the
data. As preprints gain broader adoption, the tension between
establishing primacy and the completeness of the preprint may test the
policies of preprint-friendly journals.

A second area of concern is whether a preprint can be used to support a
grant proposal. Given the length limitations placed on grant proposals
by funding agencies, there is a push to cite previous work to indicate a
research team's competence in an area or to provide preliminary data.
The National Institutes of Health (NIH) recently released a notice
clarifying their position on the use of preprints and synthesizing
feedback that they received as part of a request for information (5). In
this notice, the NIH indicated that preprints can be cited anywhere that
other research is cited including research plans, bibliographies,
biosketches, and progress reports. Some fear that the use of preprints
will allow scientists to circumvent page limits by posting preliminary
manuscripts (24). One would hope that both consumers of preprints and
grant proposal reviewers would be able to differentiate between someone
trying to game the system and someone that is using preprints as a
mechanism to improve their science. This would be greatly facilitated by
following the NIH recommendation of using preprints as evidence for
research progress, but providing an indication that the preprints are
not peer-reviewed publications (5). This would help review panels in
rendering their decisions and help authors substantiate their
preliminary data.

A third concern is what role preprints should have in assessing a
scientist's productivity. Clearly use of publication metrics as an
indicator of a scientist's productivity and impact is a contentious
topic without even discussing the role of preprints. Regardless, given
the propensity for researchers to list manuscripts as being ``in
preparation'' or ``in review'' on an application or curriculum vitae,
listing them instead as preprints that can be reviewed by a committee
would significantly enhance an application and a reviewer's ability to
judge the application. In fact, several funding agencies including the
NIH, Wellcome Trust, UK Medical Research Council encouraging fellowship
applicants to include preprints in their materials (5).

Beyond these concerns, preprints are also causing some to change their
publication goals. Some authors are explicitly stating that a preprint
will not be submitted to a journal (25). Although these authors may be a
minority of those who post preprints, such an approach may be attractive
to those who need to cite a report of a brief research communication, a
critique of another publication, or negative results. It is clear that
the adoption of preprints will challenge how scientists interact and
evaluate each other's work. There is great potential to empower
researchers by controlling when a citable piece of work is made public.

\textbf{\emph{Microbiology anecdotes.}} The peer-review editorial
process can be lengthy and adversarial. Because preprints are public and
freely available they represent a rapid and potentially collaborative
method for disseminating research. Several anecdotes from the
microbiology literature are emblematic of benefits of the rapid release
cycle that is inherent in the use of preprints.

First, preprints have proven useful for rapidly disseminating results
for disease outbreaks and new technologies. Prior to the recent Zika
virus outbreak there were approximately 50 peer-reviewed publications
that touched on the biology and epidemiology of the virus; as of April
2017 the number of Zika virus-related peer-reviewed publications was
over 2,300. During the recent outbreak, more than 150 Zika virus-related
preprints have been posted at \emph{bioRxiv}. Any manuscript that was
formally published went through several month delays in releasing
information to health care workers, the public, and scientists needing
to learn new methods to study a previously obscure virus. In contrast,
those that posted their work as a preprint were able to disseminate
their methods and results instantly. Another interesting use of
preprints to disseminate new information about Zika virus has been the
posting of a preprint describing the Zika virus outbreak in the US
Virgin Islands that will be continually updated as new data and analyses
are performed (26). Over the last several years there have also been
rapid advances in DNA sequencing technologies that have fundamentally
changed how microbial science is performed. One notable technology, the
MinIon sequencing platform from Oxford Nanopore, has received
considerable attention from researchers who have posted more than 110
preprints describing new MinIon-based methods and results to preprint
servers. For such a rapidly developing technology, the ability to share
and consume methods from other scientists has created a feed forward
effect where the technology has likely advanced at a faster rate than it
otherwise would have.

Second, preprints have proven useful for rapidly correcting the
scientific literature. On February 9, 2015, \emph{Cell Systems}
published a study that collected and analyzed metagenomic sequence data
from the New York City subway system and reported finding \emph{Yersinia
pestis} and \emph{Bacillus anthracis} (27). Because of the focus on
these two bioterrorism agents, this study generated a considerable
amount of media attention. On April 25, 2015, Petit et al. (28) posted a
preprint to Zenodo demonstrating that there was no evidence for \emph{B.
anthracis} in the dataset. On July 29, 2015, a critique was published by
\emph{Cell Systems} along with a response from the original authors
offering a correction to their manuscript (29, 30). A second anecdote of
using preprints to aid in post-publication peer-review surrounds the
publishing of a draft tardigrade genome in \emph{The Proceedings of the
National Academy of Sciences}. On November 23, 2015 a study by Boothby
et al. (31) was published online. The authors claimed that 17.5\% of its
genes came from bacteria, archaea, fungi, plants, and viruses. Another
group had been analyzing sequence data from a parallel tardigrade genome
sequencing project and did not observe the same result. A week later, on
December 1, 2015, the second group posted a preprint comparing the two
genome sequences and demonstrating that the exciting claims of
horizontal gene transfer were really the product of contaminants (32);
this analysis would eventually be peer-reviewed and published online by
the original journal on March 24, 2016 followed by a rebuttal by the
original authors on May 31, 2016 (33, 34). Two other analyses of the
original data were peer-reviewed and published in May 2016 and a third
was posted as a preprint on February 2, 2016 (35--37). Both of these
anecdotes underscore the value of having a rapid posting cycle to
correcting errors in the scientific literature and that results posted
to preprint servers were able to correct the record within weeks of the
initial publication while the traditional peer-review path took six
months in both cases. A final notable case where preprints have
accelerated the correction of the scientific record was a preprint
posted by Bik et al. (38) reporting numerous cases of image manipulation
in peer-reviewed studies. This was a case where a journal may have been
reluctant to publish the findings because it could have put the journal
in a bad light. Posting the manuscript as a preprint removed potential
conflicts of interests from journals that could have hindered its
ability to be formally published in a journal. After the preprint was
posted on April 20, 2016 it was peer-reviewed and published in
\emph{mBio} on June 7, 2016 (39). Instead of using preprints to react to
published papers that have been through peer-review, it would be
interesting to consider how the editorial process for these examples and
the infamous ``Arsenic Life'' paper (40) would have been different had
they initially been posted as preprints.

\textbf{\emph{Metrics for microbiology-affiliated preprints.}} To
analyze the use of preprints, I downloaded the \emph{bioRxiv} on April
17, 2017. I chose to analyze \emph{bioRxiv} preprints because these
preprints are amenable for submission to ASM journals and there were
9,780 \emph{bioRxiv} preprints compared to the 2,911 preprints that were
available at \emph{PeerJ Preprint} on the same date. The code used to
analyze these preprints and the rest of this manuscript are available as
a reproducible GitHub repository at
\url{http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017}.
Among the 9,780 preprints on bioRxiv, 483 were assigned by the authors
into the Microbiology category. One limitation of the \emph{bioRxiv}
interface is the inability to assign manuscripts to multiple categories
or to tag the content of the preprint. For example, this manuscript
could be assigned to either the Microbiology or the Scientific
Communication and Education categories. To counter this limitation, I
developed a more permissive approach that classified preprints as being
microbiology-affiliated if their title or abstract had words containing
\emph{yeast}, \emph{fung}, \emph{viral}, \emph{virus}, \emph{archaea},
\emph{bacteri}, \emph{microb}, \emph{microorganism}, \emph{pathogen}, or
\emph{protist}. I identified 1,617 additional manuscripts that I
considered microbiology-affiliated. These microbiology-affiliated
preprints were primarily assigned to the Evolutionary Biology (N=283),
Bioinformatics (N=237), or Genomics (N=231) categories.
